Report on Late Winter2013 Production: Image Differencing

### 2013-03-26 W13report.tex

@@

>>>>

{\bf good point: note that the curves nfp vs. threshold are
  correlated, its a cumulative distribution}.

@@

\clearpage
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{5}{|c|}{WCS RMS in mas at various stages} \\
\hline
Sensor    & Deep & Science &  Deep to Science & Coadd to Science \\
\hline
R22:S00&21&29&19&382\\ 
R22:S10&13&22&22&389\\
R22:S20&7&18&21&375\\
R22:S01&13&25&21&86\\
R22:S11&6&17&20&81\\
R22:S21&8&19&20&382\\
R22:S02&8&17&20&178\\
R22:S12&9&20&20&78\\
R22:S22&7&21&21&389\\
\hline
\end{tabular}
\caption{We looked at the resulting RMS from WCS fitting on the deep exposure alone, the science exposure alone,
fitting the deep exposure to the science exposure, and fitting a warped coadd to the science exposure.  Fitting 
the coadd to the science exposure produces an order of magnitude more scatter in the fit than at any other point.\label{tab-wcsrms}}
\end{table}
\clearpage
